\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-29 paper.qmd
Update the five Gaussian cluster 2D layout with saved figures
Update the views of Five Gaussian clusters

## A curious difference between t-SNE and UMAP revealer

@@

>>>>

## A curious difference between t-SNE, UMAP and PaCMAP revealer

@@

::: {#fig-gau-tsne-sc layout-ncol="3" fig-pos="H"}
![](figures/five_gau_clusters/tsne_layout.png)

![](figures/five_gau_clusters/2d_model_tsne.png)

::: {#fig-gau-umap-sc layout-ncol="3" fig-pos="H"}
![](figures/five_gau_clusters/umap_layout.png)

![](figures/five_gau_clusters/2d_model_umap.png)

::: {#fig-gau-pacmap-sc layout-ncol="3" fig-pos="H"}
![](figures/five_gau_clusters/pacmap_layout.png)

![](figures/five_gau_clusters/2d_model_pacmap.png)

### 2024-06-29 paper.tex
Update the five Gaussian cluster 2D layout with saved figures
Update the views of Five Gaussian clusters

\section{A curious difference between t-SNE and UMAP
revealer}\label{a-curious-difference-between-t-sne-and-umap-revealer}

@@

>>>>

\section{A curious difference between t-SNE, UMAP and PaCMAP
revealer}\label{a-curious-difference-between-t-sne-umap-and-pacmap-revealer}

@@

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/five_gau_clusters/tsne_layout.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/five_gau_clusters/2d_model_tsne.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/five_gau_clusters/sc_tsne_3.png}\end{minipage}%

\caption{\label{fig-gau-tsne-sc}Screen shots of the \textbf{langevitour}
of the five Gaussian clusters dataset, shows the model with tSNE in
\pD{}, a video of the tour animation is available at
(\url{https://youtu.be/RASEE7N5MbM}).}

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/five_gau_clusters/umap_layout.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/five_gau_clusters/2d_model_umap.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/five_gau_clusters/sc_umap_3.png}\end{minipage}%

\caption{\label{fig-gau-umap-sc}Screen shots of the \textbf{langevitour}
of the five Gaussian clusters dataset, shows the model with UMAP in
\pD{}, a video of the tour animation is available at
(\url{https://youtu.be/iG4bCPkJilw}).}

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/five_gau_clusters/pacmap_layout.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/five_gau_clusters/2d_model_pacmap.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/five_gau_clusters/sc_pacmap_2.png}\end{minipage}%

\caption{\label{fig-gau-pacmap-sc}Screen shots of the
\textbf{langevitour} of the five Gaussian clusters dataset, shows the
model with PaCMAP in \pD{}, a video of the tour animation is available
at (\url{https://youtu.be/z07cKXi8EJQ}).}
